### 2017-09-21 README.Rmd
udpate readme
update README

You need API keys for Encyclopedia of Life (EOL), and Tropicos.

@@

@@

@@

```{r downstream}
downstream("Apis", db = 'itis', downto = 'Species', verbose = FALSE)
```

@@

[![ropensci](https://ropensci.org/public_images/github_footer.png)](https://ropensci.org)

>>>>

You need API keys for Encyclopedia of Life (EOL), Tropicos, IUCN, and NatureServe.

@@

	<td style="text-align:left;"><a href="http://apiv3.iucnredlist.org/api/v3/token">link</a></td>

@@

	<td style="text-align:left;">Wikipedia</td>
	<td style="text-align:left;"><code>wiki</code></td>
	<td style="text-align:left;"><a href="https://www.mediawiki.org/wiki/API:Main_page">link</a></td>

@@

```{r downstream}
downstream(as.tsn(154395), db = 'itis', downto = 'species', verbose = FALSE)
```

@@
